Machine Learning, a Review for Tree Segmentations Task

### 2024-04-10 Notebook LaTEX/Machine Learning/main.tex
>w< wdkstp

    \subsection{Tranpose Convolution Layer}
        A transpose convolution is a partial reverse of the convolution operations.

@@

\section{Computer Vision Networks}

\section{Case Study | Direct LiDAR Point Cloud Architecture}

\section{Case Study | The Deepforest Project}

@@

\bibliographystyle{plain}
% \bibliography{refs.bib}

>>>>

    \subsection{Tranpose Convolution Layer}
        A transpose convolution is not a partial reverse of the convolution operations. 
        It simply another convolution layer where parameters such as: ``\inlinecode{stride, padding, dilation}'' means different things. 
        It increase the dimension of the input signal instead of decreasing it. 
        It's usually used as a learnable upsample component inside of a Neural Network. 
        For more information visit \href{https://pytorch.org/docs/stable/generated/torch.nn.ConvTranspose1d.html}{CONV2DTRANSPOSED} for pytorch documentations.

@@

\section{Computer Vision Networks}
    \subsection{ResNet}

\section{Image Instance Segmentations}
    We introduce the problem of Image Instance Segmentations. 
    Given an image that contains objects of interests, we want: 
    \begin{enumerate}
        \item [1.] Classify objects by the categories 
        \item [2.] Segment/identify their locations on the images. 
        \item [3.] Differentiate different instance of the objects that belong to category of interest. 
    \end{enumerate}

    \subsection{Faster RCNN}
        In this section, we take a look at ``Faster RCNN'' proposed by Ren et al.\cite{ren_faster_2016}. 
        Read \href{https://www.neuralception.com/objectdetection-fasterrcnn/}{this blog post} for a quick overview of the neural network. 
        \subsubsection{Region Proposal Network}

            The RPN takes input from convolutional feature map and propose rectangular back in the original images that may contain objects of intersts. 
            It consists of a small network (referred as mini network) that slides through the convolution featuer map to produce output. 
            In paper, the mini network takes in a  tensor from the convolutional feature map as the input. 
            The output at each location is fed into two components, one for box regression, and the other one for box classifications. 
            The feature maps are low dimensional laten features produced by any generic vision networks.
            \par
            The pytorch implementations of the Region proposal network can be found \href{https://github.com/pytorch/vision/blob/5181a854d8b127cf465cd22a67c1b5aaf6ccae05/torchvision/models/detection/rpn.py}{here}. 
            In MATLAB, it's implemented as one single atomic component and it's made by the function \href{https://www.mathworks.com/help/vision/ref/nnet.cnn.layer.regionproposallayer.html}{\inlinecode{regionProposalLayer}}.

\section{Case Study | The Deepforest Project}
\section{Case Study | Direct LiDAR Point Cloud Architecture}

@@

\bibliographystyle{plain}
\bibliography{MLGeneral.bib}
